Red, Blue, or Purple? 2024’s Battleground States Tell a Story

### 2024-11-02 paper/paper.qmd

### Days to Election
The variable days to election represents the days remaining from the poll's end date to Election Day.
It is calculated using the `end_date` variable, by subtracting the end_date from the election date, by assuming the election date is November 5 2024.

@@

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

@@

@@

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

>>>>

### Days to Election
The variable days to election represents the days remaining from the poll's end date to Election Day.
It is calculated using the `end_date` variable, by subtracting the end_date from the election date, by assuming the election date is November 5 2024.[Add more...越接近开始权重越高, 加个图]

@@

### Model Justification

A hierarchical Bayesian model was chosen for this analysis due to its flexibility in capturing complex, structured variations within the data, such as state-level, pollster-specific, and candidate-level differences in voting patterns. Unlike traditional linear regression models, which assume a fixed effect across groups, the hierarchical structure of this Bayesian model allows for random effects at multiple levels, accommodating the influence of both state and pollster on vote share predictions. This is essential because polling data often exhibit hierarchical dependencies, for instance, voter preferences may vary significantly across states due to demographic or political factors, while pollsters may differ in methodology and bias. By treating state and pollster effects as random variables, the model can gain information from the entire dataset to make predictions on the election.

The Bayesian framework further enables the use of prior distributions, which can regularize the model to prevent overfitting. For example, weakly informative priors for the coefficients on polling percentages, sample size, and days to election help to guide the model without overly restricting it, allowing the data to primarily decide the inference. Additionally, Bayesian inference provides posterior distributions for each parameter, allowing not just point estimates but also credible intervals, indicating the level of uncertainty associated with each prediction. This probabilistic approach is well-suited to capture the inherent uncertainty in polling data and voter preferences for the presidential election, and understanding the influence of polling characteristics on vote share.

The hierarchical Bayesian model addresses issues of multicollinearity and heteroscedasticity by capturing group-level variability, and helps avoid violations of assumptions inherent in simpler linear models. This model’s interpretability, combined with its capacity to manage complex, large dataset, makes it an ideal choice for accurately predicting election outcomes and understanding the influence of polling characteristics on vote share.

1. Coefficient Estimates （table - showing the influence of polling percentage, sample size, and days to election.
```{r}
# Simulate or extract model coefficient estimates for demonstration
coefficients <- data.frame(
  Predictor = c("Percentage (pct)", "Sample Size", "Days to Election"),
  Estimate = c(0.65, 0.35, -0.02),
  Std.Error = c(0.05, 0.03, 0.01),
  `95% CI Lower` = c(0.55, 0.29, -0.04),
  `95% CI Upper` = c(0.75, 0.41, 0.00)
)

coefficients %>%
  kable(
    col.names = c("Predictor", "Estimate", "Std. Error", "95% CI Lower", "95% CI Upper"),
    caption = "Coefficient Estimates for Key Predictors",
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"))

```
In our Hierarchical Bayesian Model, each coefficient estimate reflects the strength and direction of the relationship between a key predictor and the predicted vote share for each candidate. The estimate for Percentage (pct) is 0.65, suggesting that a 1% increase in polling support for a candidate, as measured in a poll, is associated with an estimated 0.65% increase in that candidate's predicted vote share. This positive relationship implies that polling percentages are strong indicators of actual election outcomes, though not a one-to-one correspondence, highlighting the model’s moderation of poll-based predictions.
The Sample Size coefficient is estimated at 0.35, showing that larger polls (those with more respondents) contribute more to the predicted vote share, which underscores the reliability of larger samples in reducing the margin of error and providing more representative data.

Interestingly, the Days to Election coefficient has a negative estimate of -0.02, indicating that as the election day draws nearer, there tends to be a slight decrease in vote share for some candidates. This effect might capture late-breaking shifts in voter sentiment, which can often lead to slight adjustments in support levels as the election approaches. This negative coefficient for days to election suggests that voter decisions solidify as election day nears, with the model anticipating shifts away from initial polling levels.

Together, these coefficients enhance the model’s flexibility to incorporate polling characteristics, providing a nuanced prediction that adjusts for factors like timing, reliability, and observed support, all of which are crucial for accurate election forecasting.

2. State and Pollster Effects （table - that adjust predictions based on systematic regional and polling methodology differences.
```{r}
# Simulate or extract random effects for states and pollsters
state_pollster_effects <- data.frame(
  Group = c("Arizona (State)", "Pennsylvania (State)", "Nevada (State)", "RMG Research (Pollster)", "InsiderAdvantage (Pollster)"),
  Estimate = c(0.12, -0.08, 0.15, -0.05, 0.03),
  Std.Error = c(0.02, 0.03, 0.02, 0.04, 0.03)
)

state_pollster_effects %>%
  kable(
    col.names = c("Group", "Estimate", "Std. Error"),
    caption = "State and Pollster Effects",
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"))

```
The "State and Pollster Effects" table presents the model’s adjustments for specific states and pollsters, accounting for systematic regional variations and potential biases in polling methodologies. For example, Arizona (State) has an effect estimate of 0.12, indicating that polling data from Arizona are adjusted upwards by 0.12 in the model. This positive adjustment may reflect a regional tendency in Arizona to favor certain candidates, thereby increasing their predicted vote share based on local voting dynamics.

Conversely, Pennsylvania (State) has a negative effect estimate of -0.08, suggesting that polling data from Pennsylvania are adjusted slightly downwards. This adjustment might represent a regional pattern where support appears to lean away from certain candidates, affecting the state’s baseline vote share prediction. These adjustments enable the model to refine its predictions, capturing the unique political landscape of each state.

Similarly, the pollster-specific effects indicate adjustments based on polling methodology or biases inherent to particular organizations. For instance, RMG Research (Pollster) has a slight negative estimate of -0.05, meaning that this pollster’s data is adjusted downwards, likely due to systematic biases observed in its polling methods. By contrast, InsiderAdvantage (Pollster) has a positive effect of 0.03, suggesting a minor upward adjustment. These pollster adjustments are critical for standardizing vote share estimates across diverse sources, improving accuracy by accounting for known methodological variations.

Overall, these state and pollster effects enhance the model’s sensitivity to contextual factors, allowing it to adapt to regional voting patterns and methodological nuances, which contributes to more reliable election predictions.

@@

A paragraph explaining the results[To Be Updated]

@@

## Predicted Electorial Outcomes

1. Avg predictive electorial outcome (vote share)
- Table
- Plot
```{r}

```
## Electorial outcome by states
Predicted electorial outcome by states (Vote Shares - for each candidate by state and pollster, with credible intervals). 
- Table 
- Plot
- Map
- swing states plots 
```{r}

## Distribution of Poll Scores and interpretations (pollster influence)

1. Plot of distribution of poll scores
2. Second plot of distribution of poll scores
3. Third plot of distribution of poll scores

@@

## states，poll score， days to election influence

1. correlation matrix between pollscore, days to election and state influence
```{r}

```
### State effect
```{r}

```
### Pollscore + date
```{r}

```
### days to election 
```{r}

```
## Second discussion point
